---
title: "Project_1"
author: "Grace Rogers"
date: "3/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ISLR)
library(readxl)
library(tidyverse)
library(resampledata)
library(knitr)
library(dplyr)
library(moderndive)
library(gapminder)
library(skimr)
library(car)
library(MASS)
```

```{r}
Housing <- read_excel("Housing.xlsx")
skim(Housing)
```

```{r}
pairs(~Housing$price+Housing$size+Housing$lot+Housing$bath+Housing$bedrooms+Housing$yearbuilt+Housing$agestandardized+Housing$garagesize)

```

```{r}
Housing %>%
  select(price,size,lot,bath,bedrooms,yearbuilt,agestandardized,garagesize) %>%
  cor()

```


```{r}
Housing_model1_everything<-lm(price~.,data=Housing)
summary(Housing_model1_everything)
```
taking out id variable die to it not being relevant to the model.  age standardized is an odd variable


```{r}
Housing_model2<-lm(price~.-id,data=Housing)
summary(Housing_model2)
```
Taking out yearbuilt die to having largest probability of not being significant
```{r}
Housing_model3<-lm(price~.-id-yearbuilt,data=Housing)
summary(Housing_model3)
```
Age standardized is now working as a predictor. Removing bath die to being insignificant
```{r}
Housing_model4<-lm(price~.-id-yearbuilt-bath,data=Housing)
summary(Housing_model4)
```

Removing garage size due to being insignificant predictor
```{r}
Housing_model5<-lm(price~.-id-yearbuilt-bath-garagesize,data=Housing)
summary(Housing_model5)
```
Status and neighborhoods some are significant values while others are not. leaving the variables in for now.




