---
title: "Project 1 final"
author: "Grace Rogers and Daniel Short"
date: "4/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(readxl)
library(knitr)
library(dplyr)
library(stats)
library(skimr)
library(car)
```

# 1 
## Data Summary

```{r, echo= FALSE}
Housing <- read_excel("Housing.xlsx")
skim(Housing)
```

Upon inspecting the data, there do not seem to be any values missing in any of the rows. One concern that arised with this initial inspection is that there are many different units of measurement in the predictors. For instance, the size of the house is in thousands of square feet as the lot size is measured as a rank compared to the other lot sizes in the data set.

# 2
## Exploratory Data Analysis
We then examined the predictors using the correlation to the price of a house. Using the pairs function produced the plots below. This initial plotting shows that the year built, the lot size, and the number of bedrooms may be strong predictors of house price. These plots were a good way to get an overview of the predictors, but some of the pair plots such as the elementary school variable and status variable were not clear in showing the relationship between them and house price.

```{r, echo = FALSE}
attach(Housing)
pairs(~price+size+lot+bath+bedrooms)
pairs(~price+yearbuilt+agestandardized+garagesize)
pairs(~price +as.factor(status)+as.factor(elem))
```

We then decided to view the correlation between the predictors and the house price. This gave us a better idea of what variables may be good predictors. We see that the number of bedrooms has a negative relationship with price as garage size has a positive relationship with house price. Based on the initial results the variables lot, garage size, elem, size, bath, bedrooms, and status seemed to be the most influential factors that affected the price of the house.

```{r}
Housing$elemfactor <- as.numeric(as.factor(elem))
Housing$statusfactor <- as.numeric(as.factor(status))
Housing %>%
  select(price,size,lot,bath,bedrooms,yearbuilt,agestandardized,garagesize, elemfactor, statusfactor) %>%
  cor()
```

# 3
## Initial modeling

Based on the initial results the variables Lot, garage size, elem, size, bath, bedrooms, and status seemed to be the most influential factors that affected the price of the house. After running the model we removed a few of the variables. we removed the bath and bedroom predictors due to insignificance. For the elementary school district and status predictors, we found that some of them were significant and others were not so we left them in the initial model. The VIF numbers for the predictors were low so there was little redundancy.

```{r}
Housing_model1_rough<-lm(price~ lot+garagesize+elem+size+bath+bedrooms+status+elem,data=Housing)
summary(Housing_model1_rough)
vif(Housing_model1_rough)
```


```{r}
Housing_model2_rough<-lm(price~ lot + garagesize + elem + status, data=Housing)
summary(Housing_model2_rough)
vif(Housing_model2_rough)

```
# 4
## Model Modification

After the initial modeling, the $R^2$ value was not as high as we wanted. Since the four predictors from the model above were our best predictors, we decided to continue to explore these predictors. One idea was that the elementary school area may have an influence on the status of the house so we created an interaction term between elem and status.

```{r}
Housing_model3_rough<-lm(price ~ lot+ garagesize + elem:status, data=Housing)
summary(Housing_model3_rough)
par(mfrow=c(2,2))
plot(Housing_model3_rough)
```

Adding this interaction increased our $R^2$ value and was significant, so we kept it in the model. Next, we modified the lot size through the use of the poly command. In our final model we introduced a polynomial of size 2 on the the lot variable.

```{r}
Housing_model_final<-lm(price ~ poly(lot,2)+ garagesize + elem:status, data=Housing)
summary(Housing_model_final)
par(mfrow=c(2,2))
plot(Housing_model_final)

```

This also increased the $R^2$ value and did not effect the plots very much. Examining the residuals vs. leverage plot it was apparent that there were many high leverage and high influence points that were skewing our model. We decided the best thing to do would be to take these points out of the data set because they were causing the model to over fit outliers. These outliers were rows 74, 4, 20, 50. After this final step we got our final model.

# 5
## Conclusions
Removing the high leverage points helped to straighten out the plots in the final model. The $R^2 = 0.5829$, which is slightly lower than the value we got with the high leverage points. This means that the final model accounts for $58.29$% of the variation in the data.
```{r}
Housing_nooutliers <- Housing[-c(74,4,20,50), ]
Housing_model_final<-lm(price ~ poly(lot,2)+ garagesize + elem:status, data=Housing_nooutliers)
summary(Housing_model_final)
par(mfrow=c(2,2))
plot(Housing_model_final)
```
The 95% confidence intervals for each of the β coefficients in the final model are: 
```{r}
confint(Housing_model_final)
```
The 95% confidence interval for the mean response in the final model is:
The 95% confidence interval of the mean predictions for the Housing data is between 196.4246 thousand and 371.2406 thousand dollars.
```{r}
predict<-c(1:72)
predict<-predict(Housing_model_final, data=Housing)
mean(predict)
sd(predict)
```

```{r}
mean(predict)+1.96*sd(predict)
mean(predict)-1.96*sd(predict)
```


The 95% prediction interval for an individual response for a hypothetical house of our choosing is below. This predicts the price of the hypothetical house to be between 210.6374 and 420.1633 thousand dollars.
```{r, warning = FALSE}
new_house <- data.frame(lot = 7, garagesize = 2, elem = "parker", status = "pen")

predict(Housing_model_final, new_house, interval="predict")

```


























